---
title: "Webscrape Boliga"
output: 
  html_document:
    keep_md: true
---

## What does it do?

This package has a few helper functions to webscrape the content of [home sales prices from Boliga](http://www.boliga.dk/salg/).

This package will try to follow the [Ethical Scraper](https://medium.com/@jamesdensmore/ethics-in-web-scraping-b96b18136f01) guidelines.

## This is how you use it

First of all, you need to install the package using devtools.

```{r instal}

library(devtools)

if(!require(boliga)){
  install_github("krose/boliga")
}

```


It is rather simple to use. You only need to do the following to scrape the actual sales prices for an area that you define on the [boliga](https://www.boliga.dk) homepage. You only need to do the following:


```{r eksempel, message = FALSE, warning = FALSE}

library(boliga)
library(dplyr)
library(ggplot2)

boliger <- boliga_webscrape_sold(min_sale_date = "2017-04-01", 
                                 max_sale_date = "2017-06-30", 
                                 type = "Fritidshus", 
                                 postal_code = 4500)

glimpse(boliger)

```

I just bought a summer house in Nykøbing Sj. so let's see how the distribution of prices is.

```{r kvmplot, message = FALSE, warning = FALSE}

ggplot(boliger, aes(pris_kvm)) +
  geom_histogram()

```



